{\Huge Supersymmetry} \\ \vspace{5mm} Lecture notes for FYS5190/FYS9190 Supersymmetry

### 2023-10-03 groups.tex
New Section 3.1 and adjust ments to following two sections

%%%
\subsection{Quotient groups}
The normal subgroup can be seen as a factor in the original group that can be divided out to form a simpler group that only retains the structure that was not in the normal group. To be more precise we need the concept of {\bf cosets}. 
\df{A {\bf left coset} of a subgroup $H\subset G$ with respect to $g\in G$ is the set of members $\{gh | h\in H\}$, and a {\bf right coset} of the subgroup is the set  $\{hg|h\in H\}$. These are sometimes written $gH$ and $Hg$, respectively.}
For normal subgroups $H$ it can be shown that the sets of left and right cosets $gH$ and $Hg$ coincide and form a group. This is called the {\bf quotient}  or {\bf coset group} and denoted $G/H$.\footnote{Sometimes also called the {\bf factor group}. The notation $G/H$ is pronounced ``G mod H'', where ``mod'' is short for modulo.}
This has as its members all the {\it distinct sets} $\{gh|h\in H\}$, that can be generated by a $g\in G$, and has the binary operation $*$ with $\{gh|h\in H\}*\{g'h|h\in H\}=\{ (g\circ g')h| h\in H\}$. To simplify notation this can be written $gH*g'H=(g\circ g') H$.

@@

@@

@@

We have already seen multiple example of the exponential map construction, but we may ask, why use the exponential? One reason is that it gives us a natural expansion of the group around the identity element. With the parameters $\mathbf a=0$ the resulting matrix is the identity matrix, which means that the group element is the identity element $g=e$. Similarly, for an infinitesimal $d\mathbf a$ step away from the parameters of the identity we have the group elements near the identity, $g=I+ida_iX^i$ that we used to derive the generators. And now, if we apply a small finite step  $a_i$ away from the identity $g=I+i\frac{a_i}{n}X^i$ a total of $n$ times with smaller and smaller steps we will get
\[g=\left(I+i\frac{a_i}{n}X^i\right)^n. \]
By the limit definition of the exponential, for $n\to\infty$ this is the exponential map
\[g=\lim_{n\to\infty}\left(I+i\frac{a_i}{n}X^i\right)^n=\exp( ia_iX^i). \]

@@

\begin{Exercise}[]
Show that Eq.~(\ref{eq:SU2_parameterisation}) is a parametrisation of $SU(2)$.
\end{Exercise}

\begin{Exercise}[]
Show that for a subset $H\subset G,$ if $h_i \circ h_j^{-1} \in H$ for $\forall h_i, h_j\in H$, then $H$ is a subgroup of $G$.
\end{Exercise}

\begin{Exercise}[]
Show that if $H$ is a subgroup of $G$, then $h_i \circ h_j^{-1} \in H$ for $\forall h_i, h_j\in H$.
\end{Exercise}

\begin{Answer}
Since $H$ is a subgroup of $G$ then by point ii) in the definition since $h_j\in H$ we must also have $h_j^{-1} \in H$. With $h_i, h_j^{-1} \in H$ by point i) in definition $h_i  \circ h_j^{-1} \in H$.
\end{Answer}

@@

@@

\begin{Exercise}[]
Find the dimensions of the fundamental and adjoint representations of $SU(n)$.
\end{Exercise}

\begin{Exercise}[]
Find the fundamental representation for $SO(3)$ and the adjoint representation for $SU(2)$. What does this say about the groups and their algebras?
\end{Exercise}

@@

\begin{Exercise}[difficulty={3},label=ex:SU2_generators]
Find an expression for the generators of $SU(2)$ and their commutation relationships. {\it Hint:} One answer uses a composition function but this approach has some dangers, try also to derive the properties of the generators from a member of the group an infinitesimal distance from the identity.
\end{Exercise}

\begin{Answer}
A member $U$ of $SU(2)$ fulfils $UU^\dagger=I$ and has $\det U =1$ and can be written as 
\[U=\left[\begin{matrix} a+ib & c+id \\ -c+id &  a-ib \end{matrix}\right],\] 
where $a,b,c,d\in\mathbb R$ and $a^2+b^2+c^2+d^2=1$. Using a composition function here it is tempting to solve for $a=\sqrt{1-b^2-c^2-d^2}$ and let $a,b,c$ be the three free parameters if $SU(2)$. Note that solving for $b$, $c$ or $d$ is not really an option as a requirement for deriving the generators from the composition function is that the zero parameters, here $b=c=d=0$, give the identity element of the group, which is the identity matrix. However, there is a potential issue here that choosing the sign on the square root restricts the parameterisation to apply for only group members with positive real components in the upper left element, meaning that this composition function only works for part of the group. This is another example of a local description of the group.  Other parameterisations exist, however, they may have other problems such as a non-unique zero element (meaning no inverse of the composition function exists).

@@

>>>>

%%%
\subsection{Quotient groups}
The normal subgroup can be seen as a factor in the original group that can be divided out to form a simpler group that only retains the structure that was not in the normal group. To be more precise we need the concept of {\bf cosets}. 
\df{A {\bf left coset} of a subgroup $H\subset G$ with respect to $g\in G$ is the set of members $\{gh | h\in H\}$, and a {\bf right coset} of the subgroup is the set  $\{hg|h\in H\}$. These are sometimes written $gH$ and $Hg$, respectively.}
Despite the appearance of containing many of the same members we can show any two cosets are either disjoint or identical sets.

For normal subgroups $H$ it can be shown that the sets of left and right cosets $gH$ and $Hg$ coincide and form a group. This is called the {\bf quotient}  or {\bf coset group} and denoted $G/H$.\footnote{Sometimes also called the {\bf factor group}. The notation $G/H$ is pronounced ``G mod H'', where ``mod'' is short for modulo.}
This has as its members all the {\it distinct sets} $\{gh|h\in H\}$, that can be generated by a $g\in G$, and has the binary operation $*$ with $\{gh|h\in H\}*\{g'h|h\in H\}=\{ (g\circ g')h| h\in H\}$. To simplify notation this can be written $gH*g'H=(g\circ g') H$.

@@

% TODO: More examples here. Use Euclidean group

@@

%% TODO: Separate section here on unitary representations? Existence of finite-dimensional

@@

We have already seen multiple example of the exponential map construction, but we may ask, why use the exponential? One reason is that it gives us a natural expansion of the group around the identity element. With the parameters $\mathbf a=0$ the resulting matrix is the identity matrix, which means that the group element is the identity element $g=e$. Similarly, for an infinitesimal $d\mathbf a$ step away from the parameters of the identity we have the group elements near the identity, $g=I+ida_iX^i$ that we used to derive the generators. And now, if we apply a small finite step  $a_i$ away from the identity $g=I+i\frac{a_i}{n}X^i$ a total of $n$ times we will get
\[g=\left(I+i\frac{a_i}{n}X^i\right)^n. \]
By the limit definition of the exponential, with smaller and smaller steps letting $n\to\infty$ this is the exponential map
\[g=\lim_{n\to\infty}\left(I+i\frac{a_i}{n}X^i\right)^n=\exp( ia_iX^i). \]

@@

\begin{Exercise}[]
Show that Eq.~(\ref{eq:SU2_parameterisation}) is a parametrisation of $SU(2)$.
\end{Exercise}
\begin{Answer}
A matrix in $SU(2)$ has $2^2-1=3$ free parameters. Let us start with a generic $2\times2$ complex valued matrix
\[ U=\left[ \begin{matrix} \alpha & \beta \\ \gamma & \delta \end{matrix} \right]. \]
For this to be unitary we must have 
\[ U^\dagger U=\left[ \begin{matrix} \alpha^* & \gamma^* \\ \beta^* & \delta^* \end{matrix} \right]\left[ \begin{matrix} \alpha & \beta \\ \gamma & \delta \end{matrix} \right] 
=\left[ \begin{matrix} |\alpha|^2+|\gamma|^2 & \alpha^*\beta+\gamma^*\delta \\ \beta^*\alpha+\delta^*\gamma & |\beta|^2+|\delta|^2 \end{matrix} \right]
=\left[ \begin{matrix} 1 & 0 \\ 0 & 1 \end{matrix} \right].\]
Then from the off-diagonal, $\delta^*\gamma=-\beta^*\alpha$ and $\gamma^*\delta=-\alpha^*\beta$ which gives $|\delta|^2|\gamma|^2= |\alpha|^2 |\beta|^2$, and inserting from the diagonal we have $(1-|\beta|^2)|\gamma|^2= (1-|\gamma|^2) |\beta|^2$ which can be solved for $|\gamma|^2= |\beta|^2$. Similarly from the diagonal $|\delta|^2=|\alpha|^2$. We can then generically  write $\gamma=e^{i\theta}\beta$ and $\delta=e^{i\phi}\alpha$, where $\theta$ and $\phi$ are two phases. The diagonal requirement is then completely fulfilled if $|\alpha|^2+|\beta|^2=1$ and the matrix is
\[ U=\left[ \begin{matrix} \alpha & \beta \\ e^{i\theta}\beta & e^{i\phi}\alpha \end{matrix} \right]. \]
The determinant then requires $\alpha e^{i\phi}\alpha-\beta e^{i\theta}\beta=1$ which is fulfilled for a phase $\phi$ that rotates $\alpha$ to  $\alpha^*$ and a phase $\theta$ that rotates $\beta$ to $-\beta^*$. Thus we can write
\[ U=\left[ \begin{matrix} \alpha & \beta \\ -\beta^* & \alpha^* \end{matrix} \right]. \]
\end{Answer}

\begin{Exercise}[]
Show that for a subset $H\subset G,$ if $h_i \circ h_j^{-1} \in H$ for all $h_i, h_j\in H$, then $H$ is a subgroup of $G$.
\end{Exercise}
\begin{Answer}
\end{Answer}

\begin{Exercise}[]
Show that if $H$ is a subgroup of $G$, then $h_i \circ h_j^{-1} \in H$ for all $h_i, h_j\in H$.
\end{Exercise}
\begin{Answer}
Since $H$ is a subgroup of $G$ then by point ii) in the definition since $h_j\in H$ we must also have $h_j^{-1} \in H$. With $h_i, h_j^{-1} \in H$ by point i) in definition $h_i  \circ h_j^{-1} \in H$.
\end{Answer}

@@

\begin{Exercise}
Show any two (left or right) cosets are either disjoint or identical sets.
\end{Exercise}
\begin{Answer}
Let $H$ be a subgroup of $G$ and $g\in G$. For a member of the left coset $f\in gH$ then $gH=fH$ because $f\in gH$ implies that there must exist an $x\in H$ so that $gx=f$. Thus $fH=(gx)H=g(xH)$. Since $H$ is a group this means $xH=H$.  Thus every element in $G$ belong to exactly one left coset. The argument of right cosets is identical.
\end{Answer}

@@

@@

\begin{Exercise}[]
Find the fundamental representation for $SO(3)$.
\end{Exercise}

\begin{Exercise}[difficulty={3},label=ex:SU2_generators]
Find an expression for the generators of $SU(2)$ and their commutation relationships. {\it Hint:} One answer uses a composition function but this approach has some dangers, try also to derive the properties of the generators from a member of the group an infinitesimal distance from the identity.
\end{Exercise}
\begin{Answer}
A member $U$ of $SU(2)$ fulfils $UU^\dagger=I$ and has $\det U =1$ and can be written as 
\[U=\left[\begin{matrix} a+ib & c+id \\ -c+id &  a-ib \end{matrix}\right],\] 
where $a,b,c,d\in\mathbb R$ and $a^2+b^2+c^2+d^2=1$. Using a composition function here it is tempting to solve for $a=\sqrt{1-b^2-c^2-d^2}$ and let $a,b,c$ be the three free parameters if $SU(2)$. Note that solving for $b$, $c$ or $d$ is not really an option as a requirement for deriving the generators from the composition function is that the zero parameters, here $b=c=d=0$, give the identity element of the group, which is the identity matrix. However, there is a potential issue here that choosing the sign on the square root restricts the parameterisation to apply for only group members with positive real components in the upper left element, meaning that this composition function only works for part of the group. This is another example of a local description of the group.  Other parameterisations exist, however, they may have other problems such as a non-unique zero element (meaning no inverse of the composition function exists).

@@

\begin{Exercise}[]
Find the adjoint representation for $SU(2)$. Compare this to the fundamental representation of $SO(3)$.
\end{Exercise}

### 2023-10-03 superspace.tex
New Section 3.1 and adjust ments to following two sections

% Standalone document
\documentclass[notes.tex]{subfiles}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Superspace}
\label{chap:superspace}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this chapter we will introduce a very handy notation system for considering supersymmetry transformations effected by the $Q$ elements of the superalgebra, or, more correctly, the elements of the super-Poincar\'e group and their representations. This notation uses a coordinate system called superspace, and allows us to define so-called superfields as a replacement of ordinary field theory fields. This mirrors the Lorentz invariance built into relativistic field theory by using four-vectors. In order to do this we first need to know a little more about the properties of Grassman numbers.

%%%%%%%%%%%%%%%
\section{Superspace calculus}
\label{app:calc}
%%%%%%%%%%%%%%%
Grassmann numbers $\theta$ are numbers that anti-commute with each other but not with ordinary numbers. We will here use four such numbers and in addition we want to place them in Weyl spinors, indexed by $A$ and $\dot{A}$:\footnote{We can already see how this can be useful: if we consistently use $\theta^AQ_A$ and $\bar{\theta}_{\dot{A}}\bar{Q}^{\dot{A}}$ instead of only $Q_A$ and $\bar{Q}^{\dot{A}}$ in Eqs.~(\ref{eq:QQweyl})--(\ref{eq:QMweyl}) we can actually rewrite the superalgebra as an ordinary Lie algebra, but with Grassman elements, because of these commutation properties.}
\[\{\theta^A, \theta^B\} = \{\theta^A, \bar{\theta}^{\dot{B}}\} = \{ \bar{\theta}^{\dot{A}}, \theta^B\} = \{\bar{\theta}^{\dot{A}}, \bar{\theta}^{\dot{B}}\} =0.\]
From this we get the relationships:\footnote{There is no summation implied in the first line. These are of course the same relations we already used for the Weyl spinors.}
\begin{eqnarray}
\theta_A^2 &=& \theta_A \theta_A = -\theta_A \theta_A = 0, \label{eq:thetasq}\\
\theta^2 &\equiv& \theta\theta \equiv \theta^A\theta_A = -2\theta_1\theta_2,\\
\bar{\theta}^2 &\equiv& \bar{\theta}\bar{\theta} \equiv \bar{\theta}_{\dot{A}}\bar{\theta}^{\dot{A}} = 2\bar{\theta}^{\dot{1}}\bar{\theta}^{\dot{2}}.
\end{eqnarray}
Notice that if we have a function $f$ of a Grassman number, say $\theta_A$, then the all-order expansion of that function in terms of $\theta_A$, is
\begin{equation}
f(\theta_A) = a_0 + a_1 \theta_A,\label{eq:fexp}
\end{equation}
as there are simply no more terms because of (\ref{eq:thetasq}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Superspace definition]{Superspace definition}
\label{sec:superspace}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Superspace\footnote{First introduced by Salam \& Strathdee~\cite{Salam:1974jj}.} is a coordinate system where supersymmetry transformations are {\it manifest}, in other words, the action of elements in the super-Poincaré group ($SP$) are treated like Lorentz-transformations are in Minkowski space.
\df{{\bf Superspace} is an eight-dimension manifold that can be constructed from the {\bf coset space} of the super-Poincaré group ($SP$) and the Lorentz group ($L$), $SP/L$, by giving coordinates $z^\pi = (x^\mu, \theta^A, \bar{\theta}_{\dot{A}})$, $\pi=\mu,A,\dot A$, where $x^\mu$ are the ordinary Minkowski coordinates, and where $\theta_A$ and $\bar{\theta}^{\dot{A}}$ are four Grassman (anti-commuting) numbers, being the parameters of the $Q$-operators in the algebra.}

To understand what all of this means we begin by writing a general element of SP, $g\in SP$, using the exponential map defined in Section \ref{sec:lie_algebras}:
\[g = \exp[ix^\mu P_\mu + i\theta^{A} Q_A + i\bar{\theta}_{\dot{A}}\bar{Q}^{\dot{A}} + \frac{i}{2}\omega_{\rho\nu}M^{\rho\nu}],\]
where $x^\mu$, $\theta^{A}$, $\bar{\theta}_{\dot{A}}$ and $\omega_{\rho\nu}$ constitute the parametrisation of the group, and $P_\mu$, $Q_A$, $\bar Q^{\dot{A}}$ and $M_{\rho\nu}$ are the generators. We can now parametrise $SP/L$ simply by setting $\omega_{\mu\nu} = 0$.\footnote{$SP/L$ is {\it not} a coset group as defined previously, because $L$ is not a normal subgroup of $SP$, but its parametrisation still forms a vector space (the coset space) which we call superspace.} The remaining parameters of $SP/L$ are then the coordinates that span superspace.

As physicists we also want to know the dimensions of our new parameters $\theta$. To do this we first look at Eq.~(\ref{eq:QQbarweyl}):
\[\{Q_A, \bar{Q}_{\dot{B}}\} = 2\sigma^{\mu}_{A\dot{B}}P_\mu,\]
where we know that $P_\mu$ has mass dimension $[P_\mu] = M$. This means that $[Q^2] = M$ and $[Q]=M^{1/2}$. In the exponential, all terms must have mass dimension zero to make sense. This means that $[\theta Q] = 0$, and therefore $[\theta] = M^{-1/2}$.

We now want to find the effect of supersymmetry transformations (transformations by the super-Poincaré group) on the superspace coordinates, and we begin by noting that any $SP$ transformation can effectively be written in the following way without the boosts and rotations of the Lorentz group:
\[g_0(a,\alpha) = \exp[ia^\mu P_\mu + i\alpha^AQ_A +i\bar{\alpha}^{\dot{A}}\bar{Q}_{\dot{A}}],\]
because one can show that\footnote{Fortunately we are not going to do this because it is messy, but it can be done using the algebra of the group and the series expansion of the exponential function. Note, however, that the proof rests on the $P$s and $Q$s forming a closed set, which we saw in the algebra Eqs.~(\ref{eq:QQweyl})--(\ref{eq:QMweyl}).}
\begin{equation}
\exp\left[\frac{i}{2}\omega_{\rho\nu}M^{\rho\nu}\right]g_0(a,\alpha) = g_0(\Lambda a,S(\Lambda)\alpha)\exp\left[\frac{i}{2}\omega_{\rho\nu}M^{\rho\nu}\right],
\end{equation}
{\it i.e.}\ all that a Lorentz boost does is to transform spacetime coordinates by $\Lambda$ and Weyl spinors by $S(\Lambda)$, which is a spinor representation of $\Lambda$. Thus, in more colloquial terms, for the supersymmetry transformation it does not matter which reference frame we are working in, we know how the transformation changes between the frames, given by  $\Lambda a$  and $S(\Lambda)\alpha$.

We can now find the transformation of superspace coordinates under a supersymmetry transformation, just as we have seen the Minkowski coordinates transform under Lorentz transformations. It might be tempting to look at the effects of an element $g_0(a, \alpha)$ on a function on superspace coordinates, $F(z^\pi) = F(x^\mu, \theta^A, \bar{\theta}^{\dot{A}})$ just as we did for the translation group. However, the powers of the sum of generators in the infinite series will become very unwieldy and messy. Instead, we pull out the coordinate dependence from the function $F(z^\pi) = e^{iz^\pi K_\pi}f(0)$, where $K_\pi=(P_\mu,Q_A,\bar{Q}^{\dot{A}})$,  and we look at the transformation $z^\pi \to z'{}^\pi$ given by
%\footnote{If this way of thinking seems odd, imagine not knowing the effect of the translation generator $P_\mu$. With the exponential map $e^{ia^\mu P_\mu}$ the effect is $e^{ia^\mu P_\mu}e^{ix^\mu P_\mu}=e^{i(x^\mu+a^\mu) P_\mu}$ since $[P_\mu,P_\nu]=0$, and we can conclude that the effect is $x^\mu\to x'^\mu=x^\mu+a^\mu$.}

@@

In moving the problem to the exponential, we can use the power of some results on the exponentials of non-commuting quantities, in particular the Campbell-Baker-Hausdorff expansion.

@@

@@

Next, we move to the vector superfields.
\df{Given a vector superfield $V(x,\theta,\bar{\theta})$, we define the {\bf abelian supergauge transformation} as
\begin{eqnarray*}
V(x,\theta,\bar{\theta}) \to V'(x,\theta,\bar{\theta}) &=& V(x,\theta,\bar{\theta}) + i[ \Lambda(x, \theta, \bar{\theta}) -  \Lambda^\dagger(x, \theta, \bar{\theta})],
\label{eq:abelian_supergauge_vector_superfield}
\end{eqnarray*}
where the parameter of the transformation $\Lambda$ is a scalar superfield.}

@@

\begin{Exercise}
Find the expression for $V_{WZ}^2$.
\end{Exercise}

>>>>

% Standalone document
\documentclass[notes.tex]{subfiles}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Superspace}
\label{chap:superspace}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this chapter we will introduce a very handy notation system for considering supersymmetry transformations effected by the $Q$ elements of the superalgebra, or, more correctly, the elements of the super-Poincaré group and their representations. This notation uses a coordinate system called superspace, and allows us to define so-called superfields as a replacement of ordinary field theory fields. This mirrors the Lorentz invariance built into relativistic field theory by using four-vectors. In order to do this we need to know a little more about the properties of Grassman (anti-commuting) numbers. However, we begin by taking another look at the familiar four-vectors in light of what we have learnt about continuous groups and Lie algebras.

%%%%%%%%%%%%%%%
\section{An initial skirmish: four-vectors as a coset space}
\label{sec:four-vectors}
%%%%%%%%%%%%%%%
Traditionally, we are introduced to four-vectors as a record keeping device for time and space-position in Special Relativity. In this notation we introduce (greek) four-vector indices, and some (odd) rules for manipulating these.

Let us now go back to the Poincaré group and its generators in Sec.~\ref{sec:Poincare_group}, and in particular the exponential map in Eq.~(\ref{eq:Poincare_exp_map}). We here followed the conventions of four-vectors, but we could have equally well written it up using ordinary vector component notation, starting with the generators we derived for the different transformations of the group, {\it i.e.} rotations $J_i$, boosts $K_i$, time-translation $P_0$, and space-translation $P_i$.

We can now form the (right) coset of the Poincaré group $P$ with its Lorentz subgroup $L$, $P/L$. This is not a group since $L$ is not normal to $P$, however, the coset space is a vector space formed by the elements $\{ \Lambda g | \Lambda \in L\}$ where $g\in P$. As before, we parameterise a general element $g$ in the Poincaré group $P$ as
\begin{equation*}
g=\exp\left(\frac{i}{2}\omega^{\rho \sigma}M_{\rho \sigma}+ia^\mu P_\mu\right),
\end{equation*}
but keeping in mind the discussion above. Since any two cosets are either disjoint or identical, we can now represent each element in the coset space by one of the members in the coset picking the member where $\omega^{\rho \sigma}=0$ giving $\Lambda=I$. What remains in the coset is the four-dimensional translation operator $T(a)=e^{ia^\mu P_\mu}$.  Physically, this space is the set of all translations independent of reference frames (boosts and rotations), and it is equivalent (isomorphic) to the vector space formed by the four components of $a^\mu$ (parameters of the translation) since there is a one-to-one map between $a^\mu$  and the elements of the coset space. Thus we can say that the four-vectors form the coset space between the Poincaré group and the Lorentz group.

The transformation properties of four-vectors that we have learnt about can be demonstrated by the properties of the Poincaré group. It is possible to show, using only the properties of the generators and their commutators,  that with a member of the Lorentz group $\Lambda=\exp(\frac{i}{2}\omega^{\rho \sigma}M_{\rho \sigma})$ we have
\[ \Lambda T(a) = \exp\left(\frac{i}{2}\omega^{\rho \sigma}M_{\rho \sigma}\right)T(a)=T(\Lambda a) \exp\left(\frac{i}{2}\omega^{\rho \sigma}M_{\rho \sigma}\right) =T(\Lambda a) \Lambda, \]
where $\Lambda a \equiv \Lambda^\mu_{~\nu} a^\nu$ is the same Lorentz transformation of the four-vector translation parameter as the one we are accustomed to.

If we now want to see how a Lorentz transformation $\Lambda$ acts for example on a scalar function $F(x)$ -- this could be a scalar quantum field -- we can write $F(x)=\exp(ix^\mu P_\mu)F(0)$. This means that the transformation is essentially captured as $x'$ in $\Lambda\exp(ix^\mu P_\mu)= \exp(ix'^\mu P_\mu)$. Now, from the above we have
\[ \Lambda\exp(ix^\mu P_\mu)=\Lambda T(x)=T(\Lambda x) \Lambda, \]
and since the Lorentz transformation does nothing to a scalar coordinate independent quantity such as $F(0)$, we have $x'^\mu=\Lambda^\mu_{~\nu} x^\nu$, and the scalar function transforms the way we are used to under Lorentz transformations, namely $\Lambda F(x)= F(x')$. This argument can easily be extended to vector fields $A_\mu(x)$ and higher rank tensors, for example
\[ \Lambda A^\nu(x)= \Lambda^\mu_{~\nu} A^\nu(x'). \]
 The way we have defined four-vectors have built the Lorentz transformations of Special Relativity into our equations.

%\begin{eqnarray*}
%\Lambda \exp(ix^\mu P_\mu) &=& \exp\left(\frac{i}{2}\omega^{\rho \sigma}M_{\rho \sigma}\right)\exp(ix^\mu P_\mu) \\
%&=& \exp\left(\frac{i}{2}\omega^{\rho \sigma}M_{\rho \sigma}+ix^\mu P_\mu  - \frac{1}{4} \omega^{\rho \sigma}x^\mu [M_{\rho \sigma},P_\mu ]+\ldots\right)
%\end{eqnarray*}
%using the Baker-Campbell-Haussdorff expression from (\ref{eq:BKH_matrices}) and the fact that $P_\mu$ commutes with itself from (\ref{eq:poco2}). Here, all higher order terms contain the commutator between $M_{\mu\nu}$ and $P_\mu$
%\begin{equation}
%\frac{1}{4} \omega^{\rho \sigma}x^\mu [M_{\rho \sigma},P_\mu ] = \frac{i}{4} \omega^{\rho \sigma}x^\mu (g_{\rho\mu} P_\sigma - g_{\sigma \mu} P_\rho)
%= \frac{i}{4}( \omega^{\rho \sigma}x_\rho P_\sigma - \omega^{\rho \sigma}x_\sigma  P_\rho)
%= \frac{i}{2}\omega^{\rho \sigma}x_\rho P_\sigma
%\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Superspace definition]{Superspace definition}
\label{sec:superspace}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Superspace\footnote{First introduced by Salam \& Strathdee~\cite{Salam:1974jj}.} is a coordinate system where supersymmetry transformations are {\it manifest}, in other words, the action of elements in the super-Poincaré group ($SP$) are treated like Lorentz-transformations are in Minkowski space.
\df{{\bf Superspace} is an eight-dimension manifold that can be constructed from the {\bf coset space} of the super-Poincaré group, $SP$, and the Lorentz group, $L$, $SP/L$, by giving coordinates $z^\pi = (x^\mu, \theta^A, \bar{\theta}_{\dot{A}})$, $\pi=\mu,A,\dot A$, where $x^\mu$ are the ordinary Minkowski coordinates, and where $\theta^A$ and $\bar{\theta}_{\dot{A}}$ are four Grassman (anti-commuting) numbers in the form of Weyl spinors, being the parameters of the supercharges $Q_A$ and $\bar{Q}^{\dot{A}}$, respectively, in the exponential map of the superalgebra.}

To understand what all of this means we start from the same perspective as for the four-vectors in the previous section, and begin by writing a general element of SP, $g\in SP$, using the exponential map defined in Section \ref{sec:lie_algebras}:
\[g = \exp\left(ix^\mu P_\mu + i\theta^{A} Q_A + i\bar{\theta}_{\dot{A}}\bar{Q}^{\dot{A}} + \frac{i}{2}\omega_{\rho\nu}M^{\rho\nu}\right),\]
where $x^\mu$, $\theta^{A}$, $\bar{\theta}_{\dot{A}}$ and $\omega_{\rho\nu}$ constitute the parametrisation of the group, and $P_\mu$, $Q_A$, $\bar Q^{\dot{A}}$ and $M_{\rho\nu}$ are the generators. Following the same argument as above we can now parametrise the coset space $SP/L$ simply by setting $\omega_{\mu\nu} = 0$.\footnote{$SP/L$ is again {\it not} a coset group, because $L$ is not a normal subgroup of $SP$, but it still forms a vector space (the coset space) which we call superspace.} The remaining parameters of $SP/L$ are then the coordinates that span superspace.

In order for the exponential map to make sense the parameters $\theta$ need to anti-commute just like the $Q$s so that the contractions $\theta^{A} Q_A$ and $\bar{\theta}_{\dot{A}}\bar{Q}^{\dot{A}}$ follow ordinary commutation rules. Otherwise the commutation properties of the exponential map would be different order by order.
 As physicists we also want to know the dimensions of our new parameters. To do this we first look at Eq.~(\ref{eq:QQbarweyl}):
\[\{Q_A, \bar{Q}_{\dot{B}}\} = 2\sigma^{\mu}_{A\dot{B}}P_\mu,\]
where we know that $P_\mu$ has mass dimension $[P_\mu] = M$. This means that $[Q^2] = M$ and $[Q]=M^{1/2}$. In the exponential, all terms must have mass dimension zero to make sense. This means that $[\theta Q] = 0$, and therefore $[\theta] = M^{-1/2}$.

We now want to find the effect of supersymmetry transformations (transformations by the super-Poincaré group) on the superspace coordinates, and we begin by noting that any $SP$ transformation can effectively be written in the following way without the boosts and rotations of the Lorentz group:
\[g_0(a,\alpha) = \exp[ia^\mu P_\mu + i\alpha^AQ_A +i\bar{\alpha}^{\dot{A}}\bar{Q}_{\dot{A}}],\]
effectively setting $\omega_{\rho\nu}=0$, because we can again show that\footnote{Fortunately we are not going to do this because it is messy, but it can be done using the algebra of the group and the series expansion of the exponential function. Note, however, that the proof rests on the $P$s and $Q$s forming a closed set, which we saw in the algebra Eqs.~(\ref{eq:QPweyl})--(\ref{eq:QQbarweyl}).}
\begin{equation}
\exp\left[\frac{i}{2}\omega_{\rho\nu}M^{\rho\nu}\right]g_0(a,\alpha) = g_0(\Lambda a,S(\Lambda)\alpha)\exp\left[\frac{i}{2}\omega_{\rho\nu}M^{\rho\nu}\right],
\end{equation}
{\it i.e.}\ that all that a Lorentz boost does is to transform spacetime coordinates by $\Lambda$ and Weyl spinors by $S(\Lambda)$, which is the spinor representation of $\Lambda$ ($SL(2,\mathbb C)$). Thus, in more colloquial terms, for the supersymmetry transformation it does not matter which reference frame we are working in, we know how the transformation changes between the frames, given by  $\Lambda a$  and $S(\Lambda)\alpha$.

We can now find the transformation of superspace coordinates under a supersymmetry transformation, just as we have seen the Minkowski coordinates transform under Lorentz transformations. It might be tempting to look directly at the effects of an element $g_0(a, \alpha)$ on a function on superspace coordinates, $F(z^\pi) = F(x^\mu, \theta^A, \bar{\theta}_{\dot{A}})$, just as we did for the translation group. However, the powers of the sum of generators in the infinite series will become very unwieldy and messy. Instead, we pull out the coordinate dependence from the function $F(z^\pi) = e^{iz^\pi K_\pi}F(0)$, where $K_\pi=(P_\mu,Q_A,\bar{Q}^{\dot{A}})$,  and we look at the transformation $z^\pi \to z'{}^\pi$ given by

@@

In moving the problem to the exponential, we can use the power of some results on the exponentials of non-commuting quantities, in particular the Campbell-Baker-Hausdorff expansion from (\ref{eq:BKH_matrices}).

@@

%%%%%%%%%%%%%%%
\section{Superspace calculus}
\label{app:calc}
%%%%%%%%%%%%%%%
Grassmann numbers $\theta$ are numbers that anti-commute with each other but not with ordinary numbers. We will here use four such numbers and in addition we want to place them in Weyl spinors, indexed by $A$ and $\dot{A}$:\footnote{We can already see how this can be useful: if we consistently use $\theta^AQ_A$ and $\bar{\theta}_{\dot{A}}\bar{Q}^{\dot{A}}$ instead of only $Q_A$ and $\bar{Q}^{\dot{A}}$ in Eqs.~(\ref{eq:QPweyl})--(\ref{eq:QQbarweyl}) we can actually rewrite the superalgebra as an ordinary Lie algebra, but with Grassman elements, because of these commutation properties.}
\[\{\theta^A, \theta^B\} = \{\theta^A, \bar{\theta}^{\dot{B}}\} = \{ \bar{\theta}^{\dot{A}}, \theta^B\} = \{\bar{\theta}^{\dot{A}}, \bar{\theta}^{\dot{B}}\} =0.\]
From this we get the relationships:\footnote{There is no summation implied in the first line. These are of course the same relations we already used for the Weyl spinors.}
\begin{eqnarray}
\theta_A^2 &=& \theta_A \theta_A = -\theta_A \theta_A = 0, \label{eq:thetasq}\\
\theta^2 &\equiv& \theta\theta \equiv \theta^A\theta_A = -2\theta_1\theta_2,\\
\bar{\theta}^2 &\equiv& \bar{\theta}\bar{\theta} \equiv \bar{\theta}_{\dot{A}}\bar{\theta}^{\dot{A}} = 2\bar{\theta}^{\dot{1}}\bar{\theta}^{\dot{2}}.
\end{eqnarray}
Notice that if we have a function $f$ of a Grassman number, say $\theta_A$, then the all-order expansion of that function in terms of $\theta_A$, is
\begin{equation}
f(\theta_A) = a_0 + a_1 \theta_A,\label{eq:fexp}
\end{equation}
as there are simply no more terms because of (\ref{eq:thetasq}).

@@

Next, we move to the vector superfields.
\df{Given a vector superfield $V(x,\theta,\bar{\theta})$, we define the {\bf abelian supergauge transformation} as
\begin{eqnarray}
V(x,\theta,\bar{\theta}) \to V'(x,\theta,\bar{\theta}) &=& V(x,\theta,\bar{\theta}) + i[ \Lambda(x, \theta, \bar{\theta}) -  \Lambda^\dagger(x, \theta, \bar{\theta})],
\label{eq:abelian_supergauge_vector_superfield}
\end{eqnarray}
where the parameter of the transformation $\Lambda$ is a scalar superfield.}

@@

\begin{Exercise}
Derive the expression for $V_{WZ}^2$ in Eq.~(\ref{eq:V2_WZ}).
\end{Exercise}
